Uncertainty Quantification in Multiscale Models of Charge Transport in Organic Semiconductors: Influence of the Exhange-Correlation Functional

### 2025-01-24 paper.tex
caption cleanup, discussion still TODO

\begin{abstract}
This study investigates the impact of exchange-correlation functional choices on the predictive accuracy of multiscale models for charge transport in organic semiconductors (OSCs). A hybrid functional approach is applied to analyze uncertainties in key parameters influencing charge mobility, focusing on the Hartree--Fock exchange fraction . Using 2-methyl-9,10-bis(naphthalen-2-yl)anthracene (MADN) as a test system, molecular dynamics and density functional theory are combined to compute reorganization energies, site energies, and electronic coupling elements. Monte Carlo sampling quantifies the uncertainty propagation, revealing that site energy variations dominate transport property uncertainties, while coupling elements contribute minimally. The findings underscore the need for accurate parameter determination and functional selection, with implications for enhancing the reliability of first-principles-based multiscale modeling frameworks in OSC design.  
  %\bjoern{TODO}{rewrite}This work quantifies uncertainties in a multiscale model for charge dynamics in organic semiconductors (OSCs). A first-principle multiscale model integrates classical molecular dynamics (MD), density functional theory (DFT), quantum mechanical calculation and continuous-time random walk (CTRW) processes to allow the simulation of charge transport in OSCs. The model brings inherent uncertainties arising from the empirical approximations and numerical simulations. Our work particularly focusing on quantifying the uncertainty in DFT exchange-correlation functional.

%  By investigating the effects of varying Hartree-Fock (HF) levels within DFT functionals, we analyze the impact on electronic structures such as reorganization energy, molecule energy distribution, and coupling elements. The primary goal is to assess the robustness of predicting the quantity of interest (QoI), that is time-of-flight and charge mobility, under these uncertainties.

%  Monte Carlo simulations and sensitivity analysis are employed to estimate the range and confidence levels of the predicted charge mobility. As shown by Sobol indices, the QoI is most sensitive to molecule energy, then reorganization energy and least sensitive to coupling elements.  
\end{abstract}

@@

\section{Introduction}
Organic semiconductors (OSCs) are materials that consist of organic molecules, often in disordered structures formed during spin-coating or deposition processing. Besides their semiconducting properties, they are mechanically flexible and come with the potential to control charge transport properties~\cite{hamers_flexible_2001,liu_high_2015,chow_organic_2020}. This flexible functionality is achieved by tuning molecular properties to achieve an ideal operation at the device level~\cite{bronstein_role_2020, bredas_organic_2002}. Computational approaches that aim at predicting the charge transport properties of disordered molecular materials resolving the interplay between single-molecule properties (such as their electronic structure or response properties) and mesoscale material morphology can play an important role in supporting or even guiding experimental optimization processes~\cite{bronstein_role_2020, sokolov_computational_2011, grynova_read_2018}.\bjoern{add citations}{}

\begin{figure*}[tbp]
  \centering
  \includegraphics[width=\linewidth]{figs/MSM2.pdf}
  \caption{\bjoern{TODO Bjoern}{Rewrite caption}The multiscale model workflow for OSC. Step 1: MD simulation to generate atom coordinates. Step 2: Molecule energy $E_i$ calculation. Step 3: Calculation of Reorganization energy $\lambda_{ij}$ and coupling element $J_{ij}$ for pairs of molecule $i,j$ whose COM distance is less than $r_\text{cutoff}$. Step 4: Modelling dynamics on device level, such as ToF calculation.}
  \label{fig:MSM}
\end{figure*}

First-principles based multiscale models are such types of computational approaches. Due to the infeasibility of explicitly simulating the coupled non-adiabatic electron-nuclear dynamics for the time- and length scales of realistic materials, these models typically exploit the localization of electronic states in disordered molecular materials and consider a rate-based description of hopping-type transport. A popular choice for the electron transfer rate $\omega_{ij}$ between two localization sites $i$ and $j$ is Marcus theory~\cite{marcus_theory_1956, marcus_electron_1993}  ~\bjoern{add}{citation}, in which
%
\begin{equation}
    \omega_{ij} = \frac{2\pi}{\hbar} \frac{|J_{ij}|^2}{\sqrt{4\pi \lambda_{ij} k_\text{B}T}} \exp\left(-\frac{(\Delta E_{ij} - \lambda)^2}{4\lambda k_\text{B}T}\right) ,
    \label{equ:Marcus}
\end{equation}
%
where $\hbar$ is the reduced Planck constant,  $k_\text{B}$ the Boltzmann constant, and $T$ the temperature. As depicted in Fig.~\ref{fig:MSM}, given a larger scale morphology and with the definition of localization sites (Fig.~\ref{fig:MSM}(a)), multiscale models employ first-principles based methods (Fig.~\ref{fig:MSM}(b)) to explicitly calculate the remaining physical, material-specific (or rather transfer-pair-specific) quantities in Eq.~\ref{equ:Marcus}: the reorganization energy $\lambda$ (here a single value as we assume a single-component material), the electronic coupling $J_{ij}$, and the site energy difference $\Delta E_{ij} = E_i - E_j$. With all that information, charge transport is modeled as a continuous time random walk (CTRW) process on a graph $\mathbf{G}$, constructed from the localization sites and the calculated rates between them (Fig.~\ref{fig:MSM}(c)). Panel (b) of Fig.~\ref{fig:MSM} mentions some specific methods for the calculation of the quantities entering Eq.~\ref{equ:Marcus}, such as mixed quantum-classical methods for obtaining the site energies with the help of microelectrostatic methods~\cite{poelking_impact_2015, poelking_long-range_2016} \bjoern{add}{citations} or the dimer projection method for determining coupling elements~\cite{baumeier_density_2010}, as they are the ones adopted in this work. What is essential about these and alternative ones is that they typically rely on density-functional theory (DFT) calculations, either directly or as a mean to parametrize classical models. The dependence of DFT calculations on the choice of an exchange-correlation functional raises the question of how sensitive the simulated charge transport is to this choice and how certain predictions of material properties are.

Uncertainty quantification (UQ) is concept from computational science which allows for an estimation of confidence intervals for a quantity of interest (QoI) and an analysis of its sensitivity in models of a physical system that contain uncertain, maybe empirical, or noisy, parameters~\cite{sarkar_uncertainty_2017,oconnor_quantifying_2024, chernatynskiy_uncertainty_2013, suleimenova_tutorial_2021,coveney_reliability_2021, coveney_when_2021}. Many common UQ studies focus on models with (partial) differential equations, e.g., drift-diffusion equations in which the diffusivity as parameter, and assume a certain distribution for the values of the parameter(s). For the multiscale model of charge transport, it is not straightforward to cast the large variety of available exchange-correlation functionals into the role of a model parameter with some distribution. To keep the problem tractable, we focus here instead specifically on the exchange part in hybrid functionals~\cite{perdew_rationale_1996,marques_densitybased_2011}, in which a DFT model for the exchange is mixed using a weighting factor $\alpha_\text{HFX}$ with a Hartree--Fock type exchange, i.e.,
%
\begin{equation}
  E_\text{x} = \alpha_\text{HFX} E_\text{x}^\text{HF} + (1-\alpha_\text{HFX})E_\text{x}^\text{DFT}.
  \label{equ:hybrid}
\end{equation}
%
More specifically, we take as the basis the PBE0 functional~\cite{adamo_toward_1999} and scrutinize (i) how the predictions of the multiscale model of charge transport are affected by variation of $\alpha_\text{HFX}$ as a proxy for uncertainties in the choice of DFT functionals, (ii) what the level of confidence is in quantitative predictions, and (iii) what are the most sensitive quantities in the model. In this sense, Eq.~\ref{equ:hybrid} is deceptively simple. For each value of $\alpha_\text{HFX}$, the graph $G$ is constructed using the respective value of the reorganization energy, the $N_\text{mol}$ site energies, and the $N_\text{pair}$ coupling elements, and the dimensionality of the problem from the perspective of UQ is $N_\text{UQ}=1+N_\text{mol}+N_\text{pair}$, which can easily be on the order of $10^{4}-10^{5}$. We consider the simulated time-of-flight (ToF) and the associated mobility the QoI in the following (see Fig.~\ref{fig:MSM}(c)) which then are subject to uncertainties in these $N_\text{UQ}$ parameters, {\em stemming} from the variation in $\alpha_\text{HFX}$. As a prototypical system, we will study hole transport in an amorphous morphology of 2-methyl-9, 10-bis(naphthalen-2-yl)anthracene (MADN), a wide-gap semiconductor that is used extensively as an ambipolar host material in organic light-emitting diodes~\cite{ko_accurate_2019, chang_great_2017} ~\bjoern{add}{citation}.

@@

We begin with a brief discussion of the molecular parameters as they are used in different ways in the multiscale model. Figure~\ref{fig:autogen_MADN} shows the adiabatic ionization potential, reorganization energy, neutral state dipole moment, and isotropic polarizability in neutral and cationic (hole) states, respectively. The adiabatic ionization potential in Fig.~\ref{fig:autogen_MADN}(a) in principle contributes to the site energy but as it is determined per molecule-type in the system, it has no effect on the site-energy difference $\Delta E_{ij}$ in Eq.~\ref{equ:Marcus}. It is nevertheless interesting to see that it increases almost linearly over the shown range of \ahfx. In contrast, the reorganization energy as shown in Fig.~\ref{fig:autogen_MADN}(b) appears to saturate for \ahfx after an initially close to linear increase. In total, $\lambda$ is found to be in an interval between \unit[0.246]{eV} and \unit[0.316]{eV} \bjoern{need}{correct numbers here}. Panels (c) and (d) of Fig.~\ref{fig:autogen_MADN} show the dipole moment of the neutral MADN molecule and the isotropic polarizability of the neutral and cationic (hole) states, respectively, both as electrostatic properties that enter indirectly the parameterization of the microelectrostatic model. As is visible, the dipole moment is rather independent on \ahfx (note that the jump of the last shown data point appears more pronounced because of the very small scale on the $y$-axis). The isotropic polarizabilities in panel (d) exhibit a linear decrease with increasing value of \ahfx which can be attributed to an increasingly attractive effective potential from stronger the Hartree--Fock-like exchange term and consequently more strongly bound electrons as one can also see from the increaseing ionization potential in panel (a).

@@

\begin{figure*}[tbp]
  \centering
  \includegraphics[width=\linewidth]{figs/scatterE_qmmm.pdf}
  \caption{\bjoern{TODO: }{rewrite caption}Scatter plot of site energy of MADN molecules calculated from different HFX, compared to the site energy calculated from HFX=0.25 (The PBE0 functional). The brighter color near the diagonal lines indicates denser population of the molecules.  The top and right histogram show the energy distributions.}
  \label{fig:E_qmmm_MADN}
\end{figure*}

\begin{table}[tbp]
  \caption{\bjoern{TODO: }{rewrite caption}In the tested $\alpha'$ values, the second column shows the maximum of $E_i(\alpha=0.25) - E_i(\alpha')$ for all molecules. Denoting $i'$ as the index of the molecule which has maximum $E_i(\alpha=0.25) - E_i(\alpha')$ for the chosen $\alpha'$, the third column shows the energy of molecule $i'$ calculated by $\alpha=0.25$. The fourth column shows the molecule energy $E_{i'}(\alpha')$ calculated by $\alpha'$. All the energies are in unit $\unit[]{eV}$.}
  \begin{ruledtabular}
    \begin{tabular}{c c c c c c c}
    $\ahfx$ & $E_\text{min}$ & $E_\text{max}$ & $\sigma$ & $\sigma_\text{el}$ & $\sigma_\text{polar}$ &  $D_{\ahfx}$ \\%  & $E_{i_\text{max}}$ \\
    \hline
    0    & -1.11 & -0.59 & 0.08 & 0.10 & 0.04 & 0.13 \\ %&  -0.94 \\
    0.05 & -1.07 & -0.63 & 0.07 & 0.09 & 0.04 & 0.12 \\ %&  -0.94 \\
    0.10 & -1.13 & -0.61 & 0.08 & 0.10 & 0.04 & 0.13 \\ %&  -0.94 \\
    0.15 & -1.16 & -0.59 & 0.09 & 0.11 & 0.05 & 0.15 \\ %&  -0.69 \\
    0.20 & -1.12 & -0.63 & 0.08 & 0.10 & 0.05 & 0.12 \\ %&  -0.82 \\
    0.25 & -1.17 & -0.60 & 0.08 & 0.11 & 0.04 & ---  \\ %&   ---\\
    \end{tabular}
  \end{ruledtabular}
  \label{tab:maxEi}
\end{table}

@@

\begin{figure*}[tbp]
  \centering
  \includegraphics[width=\linewidth]{figs/scatterJ_all.pdf}
  \caption{\bjoern{TODO:}{rewrite caption} Scatter plot of MADN coupling element $\log_{10} J^2$ calculated from different HFX, compared to the polarization energy calculated from HFX=0.25 (The PBE0 functional). The brighter color near the diagonal lines indicates denser population of the molecules.  The top and right histogram show the energy distributions.}
  \label{fig:J_MADN}
\end{figure*}

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\linewidth]{figs/fig_network_all.pdf}
  \caption{\bjoern{TODO Zhong:}{same comments regarding the $\log_{10}$ as above; replace $\alpha$ with $\alpha_\text{HF}$.}The maximum size of the subgraphs obtained in the percolation algorithm as a function of critical value $J_c$. The molecular systems obtained by different HFX are colored according to the legend.}
  \label{fig:J_percolate}
\end{figure}

@@

\begin{table}[tbp]
\caption{\bjoern{TODO:}{rewrite}The ToF and diffusive velocity calculated by ToF along a distance $L_x = \unit[9.0]{nm}$ with and without energy disorder of the MADN system as a function of the HFX. The ToF is in unit $\unit[]{s}$ and $v_\text{ToF}$ in unit $\unit[]{m/s}$.}
\begin{ruledtabular}
  \begin{tabular}{c c c c }
        \ahfx & full & $J_{ij} \mathbb{1}(\log_{10} J^2_{ij} > -5)$ & $\Delta E_{ij} =0$ \\% & $v_\text{ToF}$(no $E$) \\
    \hline
        0.00 &  $6.4 \cdot 10^{-9}$ & $7.5 \cdot 10^{-9}$ & $1.9 \cdot 10^{-10}$ \\%& 42 \\
        0.05 & $ 7.9 \cdot 10^{-9}$ & $8.1 \cdot 10^{-9}$ & $4.1 \cdot 10^{-10}$ \\%& 20 \\
        0.10 & $ 1.6 \cdot 10^{-8}$ & $1.6 \cdot 10^{-8}$ & $4.0 \cdot 10^{-10} $ \\%& 20 \\
        0.15 & $ 3.0 \cdot 10^{-8}$ & $3.1 \cdot 10^{-8}$ & $4.0 \cdot 10^{-10} $ \\%& 25 \\
        0.20 & $ 2.1 \cdot 10^{-8}$ & $2.5 \cdot 10^{-8}$ & $4.5 \cdot 10^{-10}$ \\%& 18 \\
        0.25 & $ 9.5 \cdot 10^{-8}$ & $9.7 \cdot 10^{-8}$ & $7.2 \cdot 10^{-10}$ \\%& 11 \\
    \end{tabular}
\end{ruledtabular}
\label{tab:ToF_MADN_HFX}
\end{table}

@@

\subsection{Time-of-flight of diffusion}
As discussed the ToF is calculated from the graph with weighted edges defined by the electronic structure data $(\lambda, E_1,\ldots,E_N, J_1^2,\ldots,J_{N_\text{p}}^2)$, where $N$ is the number of molecules (vertices) and $N_\text{p}$ the number of molecule pairs (edges) in the neighbor list. We can therefore consider that $\tau = \tau(\mathbf{x})$ with $\mathbf{x}=(\lambda, E_1,\ldots,E_N, \log_{10}(J_1^2),\ldots,\log_{10}(J_{N_\text{p}}^2))$ as dependent on $M = 1+N+N_\text{p}$ parameters with uncertainty, in this case stemming from the possible choices of \ahfx in the exchange-correlation functional of the multiscale model. Note that due to the data range for the electronic coupling element as discussed in the previous section, we consider $\log_{10}(J^2)$ instead of $J^2$. For MADN, we have that $M=9765$. \bjoern{ADD:}{how many pairs? $N_\text{p}=8764$}

Because the precise distribution of the uncertainties of the $M$ parameters is not known, we consider the maximum amount of uncertainties from a maximum likelihood estimation based on the data obtained from the explicit results for the different values of \ahfx and the assumption of normal distributions. In other words, each of the parameters $x_i$ for $i=1,\ldots,M$ is assigned a normal distribution with $\mathcal{N}(\mathbb{E}(x_i),\mathbb{V}(x_i))$, with $\mathbb{E}(x_i)$ ($\mathbb{V}(x_i)$) the mean (variance) of the respective data. Then, Monte-Carlo sampling is used to obtain $N_\text{MC}=50000$ different realizations of $\mathbf{x}$, the respective time-of-flight is calculated from these samples, and the resulting distribution $P(\log_{10}(\tau))$ is statistically analyzed. Specifically, we consider four different settings: in three settings, only one of the parameters blocks $(\lambda,\left\{E\right\},\left\{\log_{10}(J^2)\right\})$ is sampled while the values of the other blocks are set to their respective mean values and we denote the resulting distributions as $P_\lambda(\log_{10}(\tau))$, $P_E(\log_{10}(\tau))$, and $P_J(\log_{10}(\tau))$, respectively. In the fourth setting, all parameters are sampled at the same time, yielding $P_\mathbf{x}(\log_{10}(\tau))$. As these distributions do not necessarily follow any specific analytic form, we estimate a $99\%$ confidence interval around the median using the equal-tailed percentile method. \bjoern{Maybe discuss somewhere:}{correlations between parameters are gone, especially in site energies, but they are (practically) uncorrelated in MADN.}

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[width=0.45\textwidth]{figs/fig_mle_MADN_withE.pdf}
  \caption{\bjoern{TODO Zhong:}{swap panels a and b}Distribution of ToFs in the multiscale modeled MADN system.
  Monte Carlo sampling with a sample size $N_\text{MC}=50000$ is used to obtain the sampled distribution. The red vertical lines indicate the lower bound and upper bound of the 99\% confidence interval around the median.
  The black circles indicate the ToF obtained using varying HFX values.
  (a) $P(\log_{10}(\tau)|E_i \text{ uncertain})$, 
  (b) $P(\log_{10}(\tau)|\lambda \text{ uncertain})$, 
  (c) $P(\log_{10}(\tau)|J_{ij} \text{ uncertain})$, 
  (d) $P(\log_{10}(\tau)|E_i, \lambda, J_{ij} \text{ uncertain})$. }
  \label{fig:mle_MADN_withE}
\end{figure}

@@

\begin{figure}[tbp]
    \centering
    \includegraphics[width=0.45\textwidth]{figs/fig_PF_plot_ave.pdf}
    \caption{\bjoern{TODO Zhong:}{remove PF label; avoid the large white space at the right; make data plot symbols a little bigger and lines a little thicker.}Electric-field dependence of the mobility $\mu$ in the multiscale modeled MADN system. The dash lines are Poole--Frenkel plots obtained with specific HFX value, and the green shadow indicates the 99\% confidence interval estimated from the MC sampling with a sample size of $N_\text{MC}=10000$.}
    \label{fig:PF_plot_ave}
\end{figure}

>>>>

\begin{abstract}
This study investigates the impact of exchange-correlation functional choices on the predictive accuracy of multiscale models for charge transport in organic semiconductors (OSCs). A hybrid functional approach is applied to analyze uncertainties in key parameters influencing charge mobility, focusing on the Hartree--Fock exchange fraction. Using 2-methyl-9,10-bis(naphthalen-2-yl)anthracene (MADN) as a test system, molecular dynamics and density functional theory are combined to compute reorganization energies, site energies, and electronic coupling elements. Monte Carlo sampling quantifies the uncertainty propagation, revealing that site energy variations dominate transport property uncertainties, while coupling elements contribute minimally. The findings underscore the need for accurate parameter determination and functional selection, with implications for enhancing the reliability of first-principles-based multiscale modeling frameworks in OSC design.  
\end{abstract}

@@

\section{Introduction}
Organic semiconductors (OSCs) are materials that consist of organic molecules, often in disordered structures formed during spin-coating or deposition processing. Besides their semiconducting properties, they are mechanically flexible and come with the potential to control charge transport properties~\cite{hamers_flexible_2001,liu_high_2015,chow_organic_2020}. This flexible functionality is achieved by tuning molecular properties to achieve an ideal operation at the device level~\cite{bronstein_role_2020, bredas_organic_2002}. Computational approaches that aim at predicting the charge transport properties of disordered molecular materials resolving the interplay between single-molecule properties (such as their electronic structure or response properties) and mesoscale material morphology can play an important role in supporting or even guiding experimental optimization processes~\cite{bronstein_role_2020, sokolov_computational_2011, grynova_read_2018}.

\begin{figure*}[tbp]
  \centering
  \includegraphics[width=\linewidth]{figs/MSM2.pdf}
  \caption{Schematic representation of the multiscale framework for simulation of charge transport: (a) a representative large-scale morphology is obtained from Molecular Dynamics. (b) Information about the molecular building blocks and the morphology are used to determine the molecular transport graph $\mathbf{G}$ for a given choice of the \ahfx via calculation of reorganization energy, site energies, and electronic couplings. (c) The time-of-flight charge mobility is simulated based on the graph.}
  \label{fig:MSM}
\end{figure*}

First-principles based multiscale models are such types of computational approaches. Due to the infeasibility of explicitly simulating the coupled non-adiabatic electron-nuclear dynamics for the time- and length scales of realistic materials, these models typically exploit the localization of electronic states in disordered molecular materials and consider a rate-based description of hopping-type transport. A popular choice for the electron transfer rate $\omega_{ij}$ between two localization sites $i$ and $j$ is Marcus theory~\cite{marcus_theory_1956, marcus_electron_1993}, in which
%
\begin{equation}
    \omega_{ij} = \frac{2\pi}{\hbar} \frac{|J_{ij}|^2}{\sqrt{4\pi \lambda_{ij} k_\text{B}T}} \exp\left(-\frac{(\Delta E_{ij} - \lambda)^2}{4\lambda k_\text{B}T}\right) ,
    \label{equ:Marcus}
\end{equation}
%
where $\hbar$ is the reduced Planck constant,  $k_\text{B}$ the Boltzmann constant, and $T$ the temperature. As depicted in Fig.~\ref{fig:MSM}, given a larger scale morphology and with the definition of localization sites (Fig.~\ref{fig:MSM}(a)), multiscale models employ first-principles based methods (Fig.~\ref{fig:MSM}(b)) to explicitly calculate the remaining physical, material-specific (or rather transfer-pair-specific) quantities in Eq.~\ref{equ:Marcus}: the reorganization energy $\lambda$ (here a single value as we assume a single-component material), the electronic coupling $J_{ij}$, and the site energy difference $\Delta E_{ij} = E_i - E_j$. With all that information, charge transport is modeled as a continuous time random walk (CTRW) process on a graph $\mathbf{G}$, constructed from the localization sites and the calculated rates between them (Fig.~\ref{fig:MSM}(c)). Panel (b) of Fig.~\ref{fig:MSM} mentions some specific methods for the calculation of the quantities entering Eq.~\ref{equ:Marcus}, such as mixed quantum-classical methods for obtaining the site energies with the help of microelectrostatic methods~\cite{poelking_impact_2015, poelking_long-range_2016} or the dimer projection method for determining coupling elements~\cite{baumeier_density_2010}, as they are the ones adopted in this work. What is essential about these and alternative ones is that they typically rely on density-functional theory (DFT) calculations, either directly or as a mean to parametrize classical models. The dependence of DFT calculations on the choice of an exchange-correlation functional raises the question of how sensitive the simulated charge transport is to this choice and how certain predictions of material properties are.

Uncertainty quantification (UQ) is concept from computational science which allows for an estimation of confidence intervals for a quantity of interest (QoI) and an analysis of its sensitivity in models of a physical system that contain uncertain, maybe empirical, or noisy, parameters~\cite{sarkar_uncertainty_2017,oconnor_quantifying_2024, chernatynskiy_uncertainty_2013, suleimenova_tutorial_2021,coveney_reliability_2021, coveney_when_2021}. Many common UQ studies focus on models with (partial) differential equations, e.g., drift-diffusion equations in which the diffusivity as parameter, and assume a certain distribution for the values of the parameter(s). For the multiscale model of charge transport, it is not straightforward to cast the large variety of available exchange-correlation functionals into the role of a model parameter with some distribution. To keep the problem tractable, we focus here instead specifically on the exchange part in hybrid functionals~\cite{perdew_rationale_1996,marques_densitybased_2011}, in which a DFT model for the exchange is mixed using a weighting factor $\alpha_\text{HFX}$ with a Hartree--Fock type exchange, i.e.,
%
\begin{equation}
  E_\text{x} = \alpha_\text{HFX} E_\text{x}^\text{HF} + (1-\alpha_\text{HFX})E_\text{x}^\text{DFT}.
  \label{equ:hybrid}
\end{equation}
%
More specifically, we take as the basis the PBE0 functional~\cite{adamo_toward_1999} and scrutinize (i) how the predictions of the multiscale model of charge transport are affected by variation of $\alpha_\text{HFX}$ as a proxy for uncertainties in the choice of DFT functionals, (ii) what the level of confidence is in quantitative predictions, and (iii) what are the most sensitive quantities in the model. In this sense, Eq.~\ref{equ:hybrid} is deceptively simple. For each value of $\alpha_\text{HFX}$, the graph $G$ is constructed using the respective value of the reorganization energy, the $N_\text{mol}$ site energies, and the $N_\text{pair}$ coupling elements, and the dimensionality of the problem from the perspective of UQ is $N_\text{UQ}=1+N_\text{mol}+N_\text{pair}$, which can easily be on the order of $10^{4}-10^{5}$. We consider the simulated time-of-flight (ToF) and the associated mobility the QoI in the following (see Fig.~\ref{fig:MSM}(c)) which then are subject to uncertainties in these $N_\text{UQ}$ parameters, {\em stemming} from the variation in $\alpha_\text{HFX}$. As a prototypical system, we will study hole transport in an amorphous morphology of 2-methyl-9, 10-bis(naphthalen-2-yl)anthracene (MADN), a wide-gap semiconductor that is used extensively as an ambipolar host material in organic light-emitting diodes~\cite{ko_accurate_2019, chang_great_2017}.

@@

We begin with a brief discussion of the molecular parameters as they are used in different ways in the multiscale model. Figure~\ref{fig:autogen_MADN} shows the adiabatic ionization potential, reorganization energy, neutral state dipole moment, and isotropic polarizability in neutral and cationic (hole) states, respectively. The adiabatic ionization potential in Fig.~\ref{fig:autogen_MADN}(a) in principle contributes to the site energy but as it is determined per molecule-type in the system, it has no effect on the site-energy difference $\Delta E_{ij}$ in Eq.~\ref{equ:Marcus}. It is nevertheless interesting to see that it increases almost linearly over the shown range of \ahfx. In contrast, the reorganization energy as shown in Fig.~\ref{fig:autogen_MADN}(b) appears to saturate for \ahfx after an initially close to linear increase. In total, $\lambda$ is found to be in an interval between \unit[0.25]{eV} and \unit[0.33]{eV}. Panels (c) and (d) of Fig.~\ref{fig:autogen_MADN} show the dipole moment of the neutral MADN molecule and the isotropic polarizability of the neutral and cationic (hole) states, respectively, both as electrostatic properties that enter indirectly the parameterization of the microelectrostatic model. As is visible, the dipole moment is rather independent on \ahfx (note that the jump of the last shown data point appears more pronounced because of the very small scale on the $y$-axis). The isotropic polarizabilities in panel (d) exhibit a linear decrease with increasing value of \ahfx which can be attributed to an increasingly attractive effective potential from stronger the Hartree--Fock-like exchange term and consequently more strongly bound electrons as one can also see from the increasing ionization potential in panel (a).

@@

\begin{figure*}[tbp]
  \centering
  \includegraphics[width=\linewidth]{figs/scatterE_qmmm.pdf}
  \caption{Panels (a)-(e): Scatter plot of site energies of the MADN system for different values of \ahfx vs the PBE0 ($\ahfx=0.25$) reference. (f) Site energy disorder $\sigma$ in \unit[]{eV} for all values of \ahfx.}
  \label{fig:E_qmmm_MADN}
\end{figure*}

\begin{table}[tbp]
  \caption{Characteristics of site energies $E$ (all in \unit[]{eV}) obtained for the different values of \ahfx : minimum ($E_\text{min}$) and maximum ($E_\text{max}$), the overall standard deviation and the contributions for static and polar calculations, as well as the largest absolute variation $D_{\ahfx}$ with respect to the PBE0 data ($\ahfx=0.25$).}
  \begin{ruledtabular}
    \begin{tabular}{c c c c c c c}
    $\ahfx$ & $E_\text{min}$ & $E_\text{max}$ & $\sigma$ & $\sigma_\text{el}$ & $\sigma_\text{polar}$ &  $D_{\ahfx}$ \\%  & $E_{i_\text{max}}$ \\
    \hline
    0    & -1.11 & -0.59 & 0.08 & 0.10 & 0.04 & 0.13 \\ %&  -0.94 \\
    0.05 & -1.07 & -0.63 & 0.07 & 0.09 & 0.04 & 0.12 \\ %&  -0.94 \\
    0.10 & -1.13 & -0.61 & 0.08 & 0.10 & 0.04 & 0.13 \\ %&  -0.94 \\
    0.15 & -1.16 & -0.59 & 0.09 & 0.11 & 0.05 & 0.15 \\ %&  -0.69 \\
    0.20 & -1.12 & -0.63 & 0.08 & 0.10 & 0.05 & 0.12 \\ %&  -0.82 \\
    0.25 & -1.17 & -0.60 & 0.08 & 0.11 & 0.04 & ---  \\ %&   ---\\
    \end{tabular}
  \end{ruledtabular}
  \label{tab:maxEi}
\end{table}

@@

\begin{figure*}[tbp]
  \centering
  \includegraphics[width=\linewidth]{figs/scatterJ_all.pdf}
  \caption{Scatter plot of electronic coupling elements of the MADN system for different values of \ahfx vs the PBE0 ($\ahfx=0.25$) reference.}
  \label{fig:J_MADN}
\end{figure*}

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\linewidth]{figs/fig_network_all.pdf}
  \caption{The maximum size of the subgraphs obtained in the percolation algorithm as a function of critical value $J_c$.}
  \label{fig:J_percolate}
\end{figure}

@@

\begin{table}[tbp]
\caption{Simulated ToF (in \unit[]{s}) for different values of \ahfx in the full graph, with an additional cutoff on $J^2$, and for the case with no energetic disorder, respectively.}
\begin{ruledtabular}
  \begin{tabular}{c c c c }
        \ahfx & full & $J_{ij} \mathbb{1}(\log_{10} J^2_{ij} > -5)$ & $\Delta E_{ij} =0$ \\% & $v_\text{ToF}$(no $E$) \\
    \hline
        0.00 &  $6.4 \cdot 10^{-9}$ & $7.5 \cdot 10^{-9}$ & $1.9 \cdot 10^{-10}$ \\%& 42 \\
        0.05 & $ 7.9 \cdot 10^{-9}$ & $8.1 \cdot 10^{-9}$ & $4.1 \cdot 10^{-10}$ \\%& 20 \\
        0.10 & $ 1.6 \cdot 10^{-8}$ & $1.6 \cdot 10^{-8}$ & $4.0 \cdot 10^{-10} $ \\%& 20 \\
        0.15 & $ 3.0 \cdot 10^{-8}$ & $3.1 \cdot 10^{-8}$ & $4.0 \cdot 10^{-10} $ \\%& 25 \\
        0.20 & $ 2.1 \cdot 10^{-8}$ & $2.5 \cdot 10^{-8}$ & $4.5 \cdot 10^{-10}$ \\%& 18 \\
        0.25 & $ 9.5 \cdot 10^{-8}$ & $9.7 \cdot 10^{-8}$ & $7.2 \cdot 10^{-10}$ \\%& 11 \\
    \end{tabular}
\end{ruledtabular}
\label{tab:ToF_MADN_HFX}
\end{table}

@@

\subsection{Time-of-flight of diffusion}
As discussed the ToF is calculated from the graph with weighted edges defined by the electronic structure data $(\lambda, E_1,\ldots,E_N, J_1^2,\ldots,J_{N_\text{p}}^2)$, where $N$ is the number of molecules (vertices) and $N_\text{p}$ the number of molecule pairs (edges) in the neighbor list. We can therefore consider that $\tau = \tau(\mathbf{x})$ with $\mathbf{x}=(\lambda, E_1,\ldots,E_N, \log_{10}(J_1^2),\ldots,\log_{10}(J_{N_\text{p}}^2))$ as dependent on $M = 1+N+N_\text{p}$ parameters with uncertainty, in this case stemming from the possible choices of \ahfx in the exchange-correlation functional of the multiscale model. Note that due to the data range for the electronic coupling element as discussed in the previous section, we consider $\log_{10}(J^2)$ instead of $J^2$. For MADN, we have $N=1000$ and $N_\text{p}=8764$ so that $M=9765$.

Because the precise distribution of the uncertainties of the $M$ parameters is not known, we consider the maximum amount of uncertainties from a maximum likelihood estimation based on the data obtained from the explicit results for the different values of \ahfx and the assumption of normal distributions. In other words, each of the parameters $x_i$ for $i=1,\ldots,M$ is assigned a normal distribution with $\mathcal{N}(\mathbb{E}(x_i),\mathbb{V}(x_i))$, with $\mathbb{E}(x_i)$ ($\mathbb{V}(x_i)$) the mean (variance) of the respective data. Then, Monte-Carlo sampling is used to obtain $N_\text{MC}=50000$ different realizations of $\mathbf{x}$, the respective time-of-flight is calculated from these samples, and the resulting distribution $P(\log_{10}(\tau))$ is statistically analyzed. Specifically, we consider four different settings: in three settings, only one of the parameters blocks $(\lambda,\left\{E\right\},\left\{\log_{10}(J^2)\right\})$ is sampled while the values of the other blocks are set to their respective mean values, and we denote the resulting distributions as $P_\lambda(\log_{10}(\tau))$, $P_E(\log_{10}(\tau))$, and $P_J(\log_{10}(\tau))$, respectively. In the fourth setting, all parameters are sampled at the same time, yielding $P_\mathbf{x}(\log_{10}(\tau))$. As these distributions do not necessarily follow any specific analytic form, we estimate a $99\%$ confidence interval around the median using the equal-tailed percentile method. \bjoern{Maybe discuss somewhere:}{correlations between parameters are gone, especially in site energies, but they are (practically) uncorrelated in MADN.}

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[width=0.45\textwidth]{figs/fig_mle_MADN_withE.pdf}
  \caption{Distribution of ToFs in the MADN system from  Monte Carlo sampling with a sample size $N_\text{MC}=50000$. The red vertical lines indicate the lower bound and upper bound of the 99\% confidence interval around the median. The black circles indicate the ToF obtained using explicit \ahfx values. Uncertainties considered are (a) in the eorganziation energy, (b) in the site energy, (c) in the coupling elements, and (d) in all simultaneously.}
  \label{fig:mle_MADN_withE}
\end{figure}

@@

\begin{figure}[tbp]
    \centering
    \includegraphics[width=0.45\textwidth]{figs/fig_PF_plot_ave.pdf}
    \caption{Electric-field dependence of the mobility $\mu$ in the multiscale modeled MADN system. The dash lines are Poole--Frenkel plots obtained with specific \ahfx values, and the green shaded area indicates the 99\% confidence interval estimated from the MC sampling with a sample size of $N_\text{MC}=10000$.}
    \label{fig:PF_plot_ave}
\end{figure}
